
\documentclass[letterpaper]{article} 
\usepackage[hmargin=1.25cm, vmargin=0.75cm]{geometry}
\usepackage{enumitem}
\pretolerance=9000
\setlength{\parindent}{0pt}


\begin{document}


\begin{center}
\begin{LARGE}
 Yi Fei Chen \\
\end{LARGE}
\begin{large}
Software Developer\\
Email: yifeichen92@gmail.com
\hfill
Github: github.com/yifeichen \\
Phone:(226)750-8292 
\hfill	
Address: Longueuil, Quebec
\end{large}
\end{center}


\par\noindent\rule{\textwidth}{0.4pt}



\begin{large}
\textbf{Skills}:\\
\end{large}
\textbf{Programming Languages}:
\begin{itemize}[leftmargin=10mm]
\item Object-Oriented Programming: Strong proficiency in Java and C++ for developing scalable and maintainable software applications.
\item Embedded Software Development: Extensive experience in using C for developing embedded systems and low-level programming.
\item Scripting Languages: Skilled in scripting with Python and Bash on Linux systems to automate tasks and streamline workflows.
\end{itemize}
\textbf{Web Development}: Knowledgeable in web development using the Grails framework for building robust and efficient web applications.\\

\textbf{Database Management}: Familiarity with MySQL and MSSQL for designing, querying, and managing relational databases. \\ \\
\textbf{Software Development Practices}:
\begin{itemize}[leftmargin=10mm]
\item Methodologies: Experienced with Agile and Scrum methodologies, including iterative development, sprint planning, and daily stand-ups.
\item Version Control: Proficient in using Git for version control, including branching, merging, and pull requests.
\item CI/CD Systems: Familiarity with Continuous Integration/Continuous Deployment (CI/CD) systems to automate build and deployment processes with Jenkins.
\end{itemize}
\textbf{Languages}:

Multilingual: Fluent in English, French, and Chinese, enabling effective communication in diverse work environments.\\



\begin{large}
\textbf{Work Experience}:
\end{large}
\begin{itemize}[leftmargin=5.5mm]
\item Software developer, Gigrow, Montreal QC, February 2020 - now
	\begin{itemize} 
	\item Debug existing code and extend new features on an ARM microcontroller. 
	\item Develop and maintain applications in a Linux environment on single-board computers,
	\item Collaborate with hardware engineers to design and implement an internal testing application for a Windows environment
	\item Write and execute unit tests and maintain the automated build system using Jenkins
	\end{itemize}
\end{itemize}

\begin{large}
\textbf{Internships}:
\end{large}
\begin{itemize}[leftmargin=*]
\item Software Developer,  RSVP Tech, Waterloo, ON, September-December, 2016
	\begin{itemize}
     \item Debugged and resolved issues in backend logic using Java
     \item Prototyping android app.
     \end{itemize}
\item Software Developer,  AppZero, Ottawa, ON, January-April, 2016
	\begin{itemize}
	\item Debug and fix issues in a C++ desktop application.
	\item Implements improvements to the user interface.
	\end{itemize}
\item Intermediate Application Developer, CIBC, Toronto, On, May-August, 2015 
\begin{itemize}
    \item Developed and maintain application code in ASP.NET.
 	\item Gathered and analyzed requirements from managers and stakeholders to design and implement new features that align with business needs.
    \end{itemize}

\end{itemize}


\begin{large}
\textbf{Education}:\\
\end{large}
University of Waterloo
\begin{itemize}[leftmargin=5.5mm]
\item Master of Applied Science in Electrical and Computer Engineering specializing in computer software \\
2017 - 2019
\item Bachelor of Software Engineering Honours Co-op\\
2012 - 2017
\end{itemize}







\end{document}